Hydra Battles and Cie

### 2021-07-29 doc/hydras.tex
moved a paragraph

Quotations of \coq{} source and answers are progressively replaced from copy-pasted \emph{verbatim} to automatically generated \emph{LaTeX} blocks, using Clément Pit-Claudel's \emph{Alectryon} tool~\cite{alectryonpaper, alectryongithub}.
Many thanks to Jérémy Damour and Théo Zimmermann who designed tools for maintaining consistency between the always evolving \coq{} modules and their documentation written in \emph{LaTeX}.

@@

>>>>

@@

Quotations of \coq{} source and answers are progressively replaced from copy-pasted \emph{verbatim} to automatically generated \emph{LaTeX} blocks, using Clément Pit-Claudel's \emph{Alectryon} tool~\cite{alectryonpaper, alectryongithub}.
Many thanks to Jérémy Damour and Théo Zimmermann who designed tools for maintaining consistency between the always evolving \coq{} modules and documentation written in \emph{LaTeX}.
